Modular flow and holographic entanglement entropy in cutoff AdS / \TTbar deformed theory

### 2021-06-21 alpha/CutoffModularFlow/draft1.tex
Update draft with outlines & update TeXplates

\addtocounter{section}{-1}
\section{Conventions}
	We try to follow the conventions of the TsT paper \textcite{Apolo:2019zai}. 
	\begin{itemize}
	\item Lightcone coordinates: $u,v = x\pm t$, similar to \cite{Apolo:2019zai}. This convention has the following features:

@@

\section{Boundary story}
	A boundary interval $\mcal{A}$ defines a denisty matrix:
	\begin{equation}
		\rho_\mcal{A}
		= \tr_{\bar{\mcal{A}}} \rho
		= e^{-\mcal{H}_\mcal{A}}
	\end{equation}
	where $\bar{\mcal{A}}$ is the complement of $\mcal{A}$ and $\mcal{H}_\mcal{A}$ is the corresponding modular Hamiltonian. $\mcal{H}_\mcal{A}$ is generically nonlocal, but in a highly symmetric background (e.g.~AdS vacuum) it might be geometrically realized and corresponds to a symmetry of the underlying quantum field theory. This is the modular flow $\xi$.

@@

	In the thermal CFT$_2$,
	\begin{equation}
	w=e^{\frac{2\pi z}{\beta}}
	\end{equation}
	From this transformation between the cylinder and the plane, we can find the "local" temperature $\tilde{\beta}$
	\begin{equation}
	\tilde{\beta}(x)=2\pi\frac{sinh[\pi(x+l_b)/\beta]sinh[\pi(x-l_b)/\beta]}{sinh(2\pi l_b/\beta)}
	\end{equation}
	After integrating out,
	\begin{equation}
	f(x)=\frac{\log(sinh\frac{\pi(l_b+x)}{\beta})-\log(sinh\frac{\pi(l_b-x)}{\beta})}{2\pi}
	\end{equation}
	\sidenote{The relation between $l_b$ and $l$ comes from the gravitational side, [no way to explain this from the field theory side]}
	\begin{equation}
	2l_b=Arccoth(\frac{r_c\cosh(lr_1/2)}{\sqrt{r_1^2+r_c^2\sinh^2(lr_1/2)}})/r_1
	\end{equation}
	where
	\begin{equation}
	r_1=\frac{2\pi}{\beta}
	\end{equation}
	is the outer horizon, and $r_c$ is the cutoff, related to the deformation parameter $\lambda$. The entanglement entropy reads,
	\begin{equation}
	S(L=2l)=\frac{\pi c}{6}(f(l)-f(-l))=\frac{c}{3}\log(\frac{r_c}{r_1}\sinh(l r_1)+\sqrt{1+\frac{r_c^2}{r_1^2}\sinh^2(l r_1)})
	\end{equation}
	The C-function is
	\begin{equation}
	C(l)=lS'(l)=\frac{c}{3}lr_1\coth(lr_1)\sqrt{\frac{r_c^2}{r_c^2+r_1^2csch^2(l r_1)}}
	\end{equation}
	\begin{equation}
	C(L)=\frac{L\pi c}{3\beta}\coth\frac{L\pi}{\beta}\sqrt{\frac{1}{1+\frac{4\pi^2\epsilon^2}{\beta^2\sinh^2\frac{L\pi}{\beta}}}}
	\end{equation}
	In CFT
	\begin{equation}
	S(L)=\frac{c}{3}\log(\frac{\beta}{\pi \epsilon}\sinh\frac{L\pi}{\beta})
	\end{equation}
	\begin{equation}C(L)=\frac{L\pi c}{3\beta}\coth\frac{L\pi}{\beta}
	\end{equation}

>>>>

\addtocounter{section}{-1}

\begin{itemize}
\item add black hole spectrum 
\item geometric picture
\item maybe consider later: SSA 
\item maybe consider later: finite size effect  
\end{itemize}

\section{Conventions}
	We try to follow the conventions of the TsT paper \textcite{Apolo:2019zai}. 
	\begin{itemize}
	\item Lightcone coordinates: $u,v = x\pm t$, similar to \cite{Apolo:2019zai}. This convention has the following features:

@@

\section{$T \bar T$ deformation and cutoff AdS}

\subsection{Brief review of the duality}

\subsection{ gravitional charges}
\subsection{black spectrum from gravitional charges}

\section{Entanglement in the boundary story}
	A boundary interval $\mcal{A}$ defines a denisty matrix:
	\begin{equation}
		\rho_\mcal{A}
		= \tr_{\bar{\mcal{A}}} \rho
		= e^{-\mcal{H}_\mcal{A}}
	\end{equation}
	where $\bar{\mcal{A}}$ is the complement of $\mcal{A}$ and $\mcal{H}_\mcal{A}$ is the corresponding modular Hamiltonian. $\mcal{H}_\mcal{A}$ is generically nonlocal, but in a highly symmetric background (e.g.~AdS vacuum) it might be geometrically realized and corresponds to a symmetry of the underlying quantum field theory. This is the modular flow $\xi$.

@@

	In the thermal CFT$_2$,
	\begin{equation}
	w=e^{\frac{2\pi z}{\beta}}
	\end{equation}
	From this transformation between the cylinder and the plane, we can find the "local" temperature $\tilde{\beta}$
	\begin{equation}
	\tilde{\beta}(x)=2\pi\frac{sinh[\pi(x+l_b)/\beta]sinh[\pi(x-l_b)/\beta]}{sinh(2\pi l_b/\beta)}
	\end{equation}
	After integrating out,
	\begin{equation}
	f(x)=\frac{\log(sinh\frac{\pi(l_b+x)}{\beta})-\log(sinh\frac{\pi(l_b-x)}{\beta})}{2\pi}
	\end{equation}
	\sidenote{The relation between $l_b$ and $l$ comes from the gravitational side, [explain through coordinate map]}
	\begin{equation}
	2l_b=Arccoth(\frac{r_c\cosh(lr_1/2)}{\sqrt{r_1^2+r_c^2\sinh^2(lr_1/2)}})/r_1
	\end{equation}
	where
	\begin{equation}
	r_1=\frac{2\pi}{\beta}
	\end{equation}
	is the outer horizon, and $r_c$ is the cutoff, related to the deformation parameter $\lambda$. The entanglement entropy reads,
	\begin{equation}
	S(L=2l)=\frac{\pi c}{6}(f(l)-f(-l))=\frac{c}{3}\log(\frac{r_c}{r_1}\sinh(l r_1)+\sqrt{1+\frac{r_c^2}{r_1^2}\sinh^2(l r_1)})
	\end{equation}
	The C-function is
	\begin{equation}
	C(l)=lS'(l)=\frac{c}{3}lr_1\coth(lr_1)\sqrt{\frac{r_c^2}{r_c^2+r_1^2csch^2(l r_1)}}
	\end{equation}
	\begin{equation}
	C(L)=\frac{L\pi c}{3\beta}\coth\frac{L\pi}{\beta}\sqrt{\frac{1}{1+\frac{4\pi^2\epsilon^2}{\beta^2\sinh^2\frac{L\pi}{\beta}}}}
	\end{equation}
	In CFT
	\begin{equation}
	S(L)=\frac{c}{3}\log(\frac{\beta}{\pi \epsilon}\sinh\frac{L\pi}{\beta})
	\end{equation}
	\begin{equation}C(L)=\frac{L\pi c}{3\beta}\coth\frac{L\pi}{\beta}
	\end{equation}
